Supporting Information: Thermal sensitivity across forest vertical profiles: patterns, mechanisms, and ecological implications

### 2022-06-27 response-to-reviews.Rmd

l.629 'we currently lack mechanistic understanding of how and why the temperature sensitivity of respiration varies across the forest vertical profile'. Other than that it varies according to the prevailing temperature difference? I think the temperature difference between upper and lower canopy positions, the theme of this review, should be mentioned in regard to this.

**Thanks for suggesting. We included the following sentence:**
**Overall, although the temperature difference between upper and lower canopy positions is important driver of respiration, we currently lack mechanistic understanding of how and why its temperature sensitivity varies across the forest vertical profile.**

### 2022-06-27 vertical-thermal-review.Rmd
rewording on Q10
@nidhivinod,  here's a little wording change related tot his commit: https://github.com/EcoClimLab/vertical-thermal-review/commit/f4f03b53812ef7fbcf96cd3359c5c31321aab11c

It's important to distinguish here between temperature sensitivity of respiration (e.g., Q10) and respiration (determined based on T and other factors). I believe the reviewer's comment was referring to respiration, as opposed to Q10.  Also, I broadened wording from Q10 to "temperature sensitivity" because T sensitivity can also be characterized as E_o.

Similar to photosynthesis, respiration tends to be higher in upper-canopy sun leaves, but its temperature sensitivity (*Q~10~* or *E~0~*) shows no definite trend along the vertical gradient.
Specifically, the temperature sensitivity of respiration can be constant within vertical profiles and in seedling sun vs. shade leaves<!--[<!--@carterExperimentalWarmingTropical2021-> @weerasingheCanopyPositionAffects2014; @bolstad_foliar_1999; @zaragoza-castellsDoesGrowthIrradiance2007 <!--@zaragoza-castellsClimatedependentVariationsLeaf2008; @xuSeasonalVariationTemperature2006->]-->, greater in upper-canopy leaves<!--[@turnbullScalingFoliarRespiration2003; @harleyEffectsLightTemperature1996]-->, or greater in the lower canopy <!--[@griffinCanopyPositionAffects2002]--> (Table `r table_leaf_metabolism`). 
This variation may be attributable to forest type, leaf traits and age [e.g., greater *Q~10~* in younger leaves, @zhouLeafageEffectsTemperature2015], or acclimation to high temperature that decreases *Q~10~* [@slotGeneralPatternsAcclimation2015; @carterExperimentalWarmingTropical2021]. 
Overall, although the temperature difference between upper and lower canopy positions is important driver of *Q~10~*, we currently lack mechanistic understanding of how and why *Q~10~* varies across the forest vertical profile.

>>>>

Similar to photosynthesis, respiration tends to be higher in upper-canopy sun leaves, but its temperature sensitivity (*Q~10~* or *E~0~*) shows no definite trend along the vertical gradient.
Specifically, the temperature sensitivity of respiration can be constant within vertical profiles and in seedling sun vs. shade leaves<!--[<!--@carterExperimentalWarmingTropical2021-> @weerasingheCanopyPositionAffects2014; @bolstad_foliar_1999; @zaragoza-castellsDoesGrowthIrradiance2007 <!--@zaragoza-castellsClimatedependentVariationsLeaf2008; @xuSeasonalVariationTemperature2006->]-->, greater in upper-canopy leaves<!--[@turnbullScalingFoliarRespiration2003; @harleyEffectsLightTemperature1996]-->, or greater in the lower canopy <!--[@griffinCanopyPositionAffects2002]--> (Table `r table_leaf_metabolism`). 
This variation may be attributable to forest type, leaf traits and age [e.g., greater *Q~10~* in younger leaves, @zhouLeafageEffectsTemperature2015], or acclimation to high temperature that decreases *Q~10~* [@slotGeneralPatternsAcclimation2015; @carterExperimentalWarmingTropical2021]. 
Overall, although the temperature difference between upper and lower canopy positions is important driver of respiration, we currently lack mechanistic understanding of how and why its temperature sensitivity varies across the forest vertical profile.
